Mechanisms of detachment in fibrillar adhesive systems

### 2022-09-24 source/tex/manuscript.tex
referee 2 comments responded and revision submitted

Let us now consider the scenario where even the leg above the joint
can undergo elastic stretching together with the hairs. When a hair
detaches from the surface, the leg undergoes an elastic recoil due
to the stored elastic energy. Suppose the leg relaxes upward by a
recoil length, $\Delta l$. For $n$ hairs in contact, the force balance
before and after a hair detaches is given respectively by:

\[
\begin{array}{c}
\stackrel[i=1]{n}{\sum}k_{h}\left(l_{h,i}-l_{h,0}\right)=k_{l}\left(l_{l}-l_{l,0}\right)\\
\stackrel[i=1]{n-1}{\sum}k_{h}\left(l_{h,i}+\Delta l-l_{h,0}\right)=k_{l}\left(l_{l}-\Delta l-l_{l,0}\right)
\end{array}
\]

Solving the above two equations for $\Delta l$, we get:

\begin{equation}
\Delta l=\frac{f_{p}}{k_{h}\left(n-1\right)+k_{l}}\label{eq:backing_deform}
\end{equation}

@@

\[
\hat{f}_{p}=\frac{f_{p}}{k_{h}w},\quad\hat{F}_{net}=\frac{F_{net}}{k_{h}w},\quad\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w},\quad\hat{s}=\frac{s}{w}
\]

Here, $\hat{f_{p}}$ is a parameter which encapsulates the hair's
adhesion force, stiffness and array density. Unless specified, positive
force values represent attraction by convention.

@@

The fibrillar adhesive pad can be detached by pulling it vertically upwards
while maintaining a constant tilt angle, $\theta$, with the surface.
This can be achieved if the joint is kept fixed. 
Equations \ref{eq:force_n_d}, \ref{eq:d_max}
and \ref{eq:simul_detach} can be used to get the resulting force-distance
curves for such a scenario.

@@

For the case of a stiff leg (tibia), we see that at small distances, all hairs
of the pad are in contact with the surface, resulting in a linear
force response. On further pulling, the hairs will start to detach
sequentially from left to right, indicated by a characteristic saw-tooth
jitter in the force curves. The hairs of the pad with a higher tilt
angle will start to detach first, followed by the ones with a lower
tilt.

For the case of a soft leg (tibia), we observe a similar effect of tilt angle
on the force curves as before. The maximum adhesion force at a particular
tilt is the same as that for the stiff leg. The saw-tooth jitter are
however minimized due to the leg's deformation, leading to a dampened
force response. Interestingly, the force abruptly drops to zero for
the angles $0.2\lyxmathsym{\textdegree}$ and $0.4\lyxmathsym{\textdegree}$.
This is an effect of the elastic recoil of the leg while each hair
loses contact during the detachment process (equation (\ref{eq:backing_deform})).
The length difference between the detached hair just before it breaks
contact and its adjacent hair is $w\sin\theta$. If the leg's recoil
length, $\Delta l>w\sin\theta$, the adjacent hair will be stretched
more than its maximum length ($l_{h,p}$), and thus will also detach,
leading to further recoil of the leg. Equation (\ref{eq:backing_deform})
shows that $\Delta l$ increases with every subsequent loss of hair
contact if $\theta$ is kept constant. This implies that, once initiated,
the leg's recoil will always be large enough to detach every remaining
hair, resulting in a spontaneous propagation of the detachment front
until the pad completely breaks contact with the surface. This is consistent with 
a recent report of catastrophic failure, due to a similar recoil effect of the measurement system,
seen in micro-fibrillar adhesives with a narrow variance of individual fibril adhesive strengths \cite{RN273}.

@@

Using the above relation together with equations \ref{eq:force_n_d},
\ref{eq:d_max} and \ref{eq:simul_detach}, we can find force-distance
curves during a free vertical pull of the adhesive pad. Since the
position of the joint will influence the net moment, we use the
ratio, $s/L$, to study its effect on the detachment forces.

@@

The force curves look qualitatively different compared to the previous
case of \emph{fixed pull}. A sharp maxima is seen, coinciding with
the point when the first hair detaches. Beyond this, the force starts
to decrease sharply and once again shows the characteristic saw-tooth
jitter as the subsequent hairs detach in sequence. Nearly identical
trend is seen for both a stiff and a soft leg (tibia). The elastic recoil
of the leg does slightly reduce the amplitude of the jitter for the
soft leg case. However, no abrupt drop in the force is seen like before.
As the hairs detach, the array gets tilted more and more, making it
less likely for the recoil length, $\Delta l$, to exceed $w\sin\theta$
and detach the next adjacent hair. Thus here, we don't see any propagation
of the detachment front when the leg is soft.

@@

Instead of a vertical pull, the adhesive pad can also be detached
by rotating it about the claw-hinge, located outside the array. Such
a mode of detachment will be driven by a moment applied by the leg (tibia)
to rotate the pad around the claw-hinge until all the hairs lose contact.
Let $s_{h}$ be the distance between the claw-hinge and the right
end of the array; $s_{l}$ be the distance between the joint
and the right end of the array. The joint is assumed to be fixed here. To illustrate the mechanism, let us
fix $s_{l}/L=1$ and $s_{h}/w=10$ and vary the vertical claw-hinge
distance, $d_{s}$. At any particular instant, the pulling force applied
by the leg, $F_{pull}=M_{net}/\left(s_{l}+s_{h}\right)$, where $M_{net}$
is obtained by setting $s=-s_{h}$ in equation (\ref{eq:moment_n_d}).
Equation (\ref{eq:force_n_d}) will give us the reaction force acting
on the claw-hinge, $F_{claw-hinge}$.

@@

Detachment by flexing requires that the claw remains fixed and stable
during the process. We see that generally, the normal load, acting
on the hinge, $F_{claw-hinge}$, follows a similar trend as $F_{pull}$ (Figure \ref{fig:Flex}).
For low values of $d_{s}$, $F_{claw-hinge}$ goes to negative values,
implying that the claw should adhere well with the surface to resist
this negative load. As the detachment progresses however, the array
starts to exert a positive load on the claw.

@@

Let us now fix $\hat{f}_{p}=0.1$ and investigate the influence of
the number of hairs, $N_{t}$, on the reduction factor (Figure \ref{fig:Reduction-factor-Nt}).
The colour plots show that high $N_{t}$ increases $r$ irrespective
of the mode of detachment. Under a tilted state, more hairs
are compressed when $N_{t}$ is high, which reduces the net adhesion.
This highlights the advantage of having a split contact design found
in many biological systems. A higher number of hairs offers a better
control over adhesion and thus is more suited for reversible attachment
and detachment during locomotion. The specific trends of reduction
factor for each mode of detachment can be understood by similar arguments
of \emph{elastic weakening}, as discussed in the previous section.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics{Reduction_factor-Nt}\caption{\textbf{Effect of $N_{t}$ on reduction factor.} 
Colour plots showing the effect of the number of hairs, $N_{t}$, on
the reduction factor for each mode of detachment. Here, we fix the
dimensionless parameter, $\hat{f}_{p}=0.1$. All values are normalized
to dimensionless forms, as described in text. \label{fig:Reduction-factor-Nt}}
\par\end{centering}
\end{figure}

@@

The above analysis illustrates how the design of the beetle's hairy
adhesive pads is suitable for modulating its adhesion. Effective control
and release of its joints can help the insect to reduce the pad's
adhesion, allowing it to detach with little effort. High reduction
in adhesion is seen when the pad is tilted relative to the surface
during detachment, as a result of \emph{elastic weakening}. To the
best of our knowledge, there is no direct experimental evidence that
beetles or any other animal can modulate its adhesion by taking advantage of this effect.
Considering that hair deformation occurs at length scales below 10
\textgreek{m}m, direct observation of this effect on running beetles
would be challenging. A recent study on PDMS micro-pillar arrays,
however, does indeed show a strong reduction in the adhesion force
due to slight misalignments with the surface \cite{RN252}. Based on
previously reported microscopic investigation of freely walking dock
beetles \cite{RN83}, we argue that the following experimental observations
provide support to our proposed model: 1) The detachment was shown
to follow a three-dimensional twist of the leg, which suggests a complex
inhomogeneous deformation of hairs across the array, leading to \emph{elastic
weakening}, which is suited for easy detachment. Similar twisting action during detachment was also observed in flies \cite{niederegger2003} and has been used to easily detach mushroom-shaped artificial adhesive arrays \cite{kang2017}.  2) The beetle can at times instantaneously detach all
its legs and drop itself while upside down. This could be explained
by the beetle freeing up its joints and using just its body weight
to provide the necessary force to detach all its legs via \emph{free
pull} (similar to path 3 above). 3) Only a fraction of the beetle's
pads made contact with the surface during locomotion, which indicates
that the pads should naturally be in a slightly tilted state. This
not only reduces the contact area, but also non-uniformly deforms
the hairs, both leading to a reduction in adhesion for easy detachment.
4) Contact images showed that the array \emph{peels} from the proximal
to distal direction during detachment. However, the beetle's hairs
are attached to a relatively stiff backing \cite{RN53}, so it wouldn't
be able to \emph{peel} its array, since peeling, strictly speaking,
depends on the elastic contribution of a thin flexible backing as
it bends during the process \cite{RN147}. Rather, the \emph{peeling}
observed in the beetle's case should be a result of the pad detaching
from the surface in a tilted orientation, causing the hairs to distinctly detach
in sequence. 5) The time scale of detachment was reported to be an
order of magnitude shorter than the attachment time scale, which could
be a result of the elastic recoil of the leg causing a spontaneous
propagation of the detachment front (Figure \ref{fig:Fixed-pull}).

There exists a limit to how much the pad can tilt, depending on its
geometry and material properties. Suppose the hair has a maximum linear
elastic strain limit, $\varepsilon_{m}$, and natural length, $l_{h,0}$.
Based on Figure \ref{fig:Schematic}, if the right most hair is compressed
to its elastic limit, one can derive from simple geometry, that, the
corresponding maximum limit in tilt angle is given by: 
\[
\theta_{limit}=\arctan\frac{l_{h,0}\varepsilon_{m}}{\left(N_{t}-1\right)w}
\]
$\theta_{limit}$ will limit the reduction factor for each of the
detachment mechanisms presented. Longer hairs can result in a lateral
collapse or bundling of hairs, imposing an additional constraint on
$\theta_{limit}$. Large deformation of hairs can also lead to buckling,
which will further limit the reduction in adhesion due to the smaller
effective modulus. Thus, the geometry of the individual hairs is also
crucial in effectively reducing adhesion by \emph{elastic weakening}.
Ideally, hairs with large diameters would be preferable to eliminate
buckling, and optimally long hairs would provide a large range of
angles to which the pad can be tilted while avoiding bundling.

@@

Inhomogeneous deformation of hairs results in significant reductions
in the adhesion of a fibrillar system similar to an insect's tarsal hairy adhesive pads. Such a condition can be achieved
by either 1) pulling the pad while maintaining a constant tilt angle,
2) pulling the pad while maintaining a free tibia-tarsus leg joint or 3) flexing
the pad around the claw. Strategic control of the joint's mobility or claw
can allow the leg to easily switch between the above mechanisms, thus
providing a simple way to reduce adhesion as per necessity. The presence
of a deformable leg can further trigger a spontaneous propagation
of hair detachment due to the leg's elastic recoil, making it suitable
for fast detachment. Arrays with low $\hat{f}_{p}$ and large number
of hairs, with a hair geometry that allows for large deformations
while avoiding buckling and lateral bundling represent the optimal
design conditions to maximize the range of control over adhesion.
The proposed model is supported by previously reported experimental
observations of leg detachment in dock beetles and highlights possible role of the joint and claws to 
enable reversible adhesion. Similar strategies could potentially be adopted in the design of bio-inspired 
artificial fibrillar adhesives to easily switch the adhesion state without the need of asymmetric structures.

>>>>

Let us now consider the scenario where even the leg above the joint
can undergo elastic stretching together with the hairs. When a hair
detaches from the surface, the leg undergoes an elastic recoil due
to the stored elastic energy. Suppose the leg relaxes upward by a
recoil length, $\Delta l$, at the point of the joint. For $n$ hairs in contact, when a hair detaches, 
the array's tilt angle will change from initial $\theta_{b}$ to $\theta_{a}$ as a result of joint rotation. 
The $i^{th}$ hair of the array thus deforms by $\Delta l_{i}$, which by geometry, is derived as:
\begin{equation}
\Delta l_{i}=\Delta l + iw\left(\tan \theta_{a}-\tan \theta_{b}\right)\label{eq:delta_li}
\end{equation}

 The force balance before and after a hair detaches is thus given respectively by:

\[
\begin{array}{c}
\stackrel[i=1]{n}{\sum}k_{h}\left(l_{h,i}-l_{h,0}\right)=k_{l}\left(l_{l}-l_{l,0}\right)\\
\stackrel[i=1]{n-1}{\sum}k_{h}\left(l_{h,i}+\Delta l_{i}-l_{h,0}\right)=k_{l}\left(l_{l}-\Delta l-l_{l,0}\right)
\end{array}
\]

Solving the above two equations with equation \ref{eq:delta_li} for $\Delta l$, we get:

\begin{equation}
\Delta l=\frac{f_{p}-k_{h}w(n/2)(n-1)\left(\tan \theta_{a}-\tan \theta_{b}\right)}{k_{h}\left(n-1\right)+k_{l}}\label{eq:backing_deform}
\end{equation}

@@

\[
\hat{f}_{p}=\frac{f_{p}}{k_{h}w},\quad\hat{F}_{net}=\frac{F_{net}}{k_{h}w},\quad\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w},\quad\hat{s}=\frac{s}{L}
\]

Here, $\hat{f_{p}}$ is a parameter which encapsulates the hair's
adhesion force, stiffness and array density. Unless specified, positive
force values represent attraction by convention. Python scripts were written to solve the above equations under specific detachment conditions (available in the public repository \url{https://github.com/PranavSudersan/paper-effect_of_tilt/blob/main/codes/Fibrillar\%20adhesion\%20-\%20Effect\%20of\%20tilt.ipynb})

@@

The fibrillar adhesive pad can be detached by pulling it vertically upwards
while maintaining a constant tilt angle, $\theta$, with the surface.
This can be achieved if the joint is kept fixed. 
Equations \ref{eq:force_n_d}, \ref{eq:d_max}
and \ref{eq:simul_detach} can be used to get the resulting force-distance
curves for such a scenario. To summarize the numerical procedure in brief, we start with an initial $n=25$ hairs. ${F}_{net}$ is then calculated for increasing ${d_{s}}$, until $d_{s}= d_{s,max}$, upon which $n$ value is decremented by 1. The above process is repeated for increasing $d_{s}$ until $n=0$, indicating complete detachment. For the case of the soft leg, on each instance when $n$ is decremented,  ${d_{s}}$ is increased by an additional $\Delta l$ value (equation \ref{eq:backing_deform}) in order to account for the recoil effect of the leg.

@@

For the case of a stiff leg (tibia), we see that at small distances, all hairs
of the pad are in contact with the surface, resulting in a linear
force response. On further pulling, the hairs will start to detach
sequentially from left to right, indicated by a characteristic saw-tooth
jitter in the force curves. The pad with a higher tilt
angle initiates hair detachment first, in comparison to a pad with a lower
tilt.

For the case of a soft leg (tibia), we observe a similar effect of tilt angle
on the force curves as before. The maximum adhesion force at a particular
tilt is the same as that for the stiff leg. The saw-tooth jitter are
however minimized due to the leg's deformation, leading to a dampened
force response. Interestingly, the force abruptly drops to zero for
the angles $0.2\lyxmathsym{\textdegree}$ and $0.4\lyxmathsym{\textdegree}$.
This is an effect of the elastic recoil of the leg while each hair
loses contact during the detachment process (equation (\ref{eq:backing_deform})).
The length difference between the detached hair just before it breaks
contact and its adjacent hair is $w\sin\theta$. If the leg's recoil
length, $\Delta l>w\sin\theta$, the adjacent hair will be stretched
more than its maximum length ($l_{h,p}$), and thus will also detach,
leading to further recoil of the leg. Equation (\ref{eq:backing_deform})
shows that $\Delta l$ increases with every subsequent loss of hair
contact if $\theta$ is kept constant (i.e. $\theta_{b}=\theta_{a}$). This implies that, once initiated,
the leg's recoil will always be large enough to detach every remaining
hair, resulting in a spontaneous propagation of the detachment front
until the pad completely breaks contact with the surface. This is consistent with 
a recent report of catastrophic failure, due to a similar recoil effect of the measurement system,
seen in micro-fibrillar adhesives with a narrow variance of individual fibril adhesive strengths \cite{RN273}.

@@

Using the above relation together with equations \ref{eq:force_n_d},
\ref{eq:d_max} and \ref{eq:simul_detach}, we can find force-distance
curves during a free vertical pull of the adhesive pad. 
A similar numerical procedure as \emph{fixed pull} is followed here. Since the
position of the joint will influence the net moment, we use the
ratio, $s/L$, to study its effect on the detachment forces.

@@

The force curves look qualitatively different compared to the previous
case of \emph{fixed pull}. A sharp maxima is seen, coinciding with
the point when the first hair detaches. Beyond this, the force starts
to decrease sharply and once again shows the characteristic saw-tooth
jitter as the subsequent hairs detach in sequence. Nearly identical
trend is seen for both a stiff and a soft leg (tibia). The elastic recoil
of the leg does slightly reduce the amplitude of the jitter for the
soft leg case. However, no abrupt drop in the force is seen like before.
As the hairs detach, the array gets tilted more and more (i.e. $\theta_{b}<\theta_{a}$), making it
less likely for the recoil length, $\Delta l$, to exceed $w\sin\theta_{a}$
and detach the next adjacent hair. Thus here, we don't see any propagation
of the detachment front when the leg is soft.

@@

Instead of a vertical pull, the adhesive pad can also be detached
by rotating it about the claw-hinge, located outside the array. Such
a mode of detachment will be driven by a moment applied by the leg (tibia)
to rotate the pad around the claw-hinge until all the hairs lose contact.
Let $s_{h}$ be the distance between the claw-hinge and the right
end of the array; $s_{l}$ be the distance between the joint
and the right end of the array. The joint is assumed to be fixed here. To illustrate the mechanism, let us
fix $s_{l}/L=1$ (here, $L=24w$) and $s_{h}/w=10$ and vary the vertical claw-hinge
distance, $d_{s}$. At any particular instant, the pulling force applied
by the leg, $F_{pull}=M_{net}/\left(s_{l}+s_{h}\right)$, where $M_{net}$
is obtained by setting $s=-s_{h}$ in equation (\ref{eq:moment_n_d}).
Equation (\ref{eq:force_n_d}) will give us the reaction force acting
on the claw-hinge, $F_{claw-hinge}$.

@@

Detachment by flexing requires that the claw remains fixed and stable
during the process. We see that generally, the normal load, acting
on the hinge, $F_{claw-hinge}$, follows a similar trend as $F_{pull}$ (Figure \ref{fig:Flex}).
For low values of $d_{s}$, $F_{claw-hinge}$ goes to negative values,
implying that the claw should stick well with the surface, perhaps by mechanical interlocking, to resist
this negative load. As the detachment progresses however, the array
starts to exert a positive load on the claw.

@@

Let us now fix $\hat{f}_{p}=0.1$ and investigate the influence of
the number of hairs, $N_{t}$, on the reduction factor (Figure \ref{fig:Reduction-factor-Nt}).
The colour plots show that high $N_{t}$ increases $r$ irrespective
of the mode of detachment. Under a tilted state, more hairs
are compressed when $N_{t}$ is high, which reduces the net adhesion.
This highlights another advantage of having a split contact design found
in many biological systems. A design comprising of a large number of hairs not only enhances the adhesion due to scaling effects \cite{Kamperman2010}, but could also offer a better
control over adhesion, making it quite suitable for reversible attachment
and detachment during locomotion. The specific trends of reduction
factor for each mode of detachment can be understood by similar arguments
of \emph{elastic weakening}, as discussed in the previous section.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics{Reduction_factor-Nt}\caption{\textbf{Effect of $N_{t}$ on reduction factor.} 
Colour plots showing the effect of the number of hairs, $N_{t}$, on
the reduction factor for each mode of detachment. Here, we fix the
dimensionless parameter, $\hat{f}_{p}=0.1$. The dimensionless parameters $\hat{d_{s}}=\frac{d_{s}-l_{h,0}}{w}$ and $\hat{s}=\frac{s}{L}$, as described in text. \label{fig:Reduction-factor-Nt}}
\par\end{centering}
\end{figure}

Figures \ref{fig:Reduction-factor_fp} and \ref{fig:Reduction-factor-Nt} can be combined into a single set of colour plots by defining a new dimensionless parameter,  $\chi=\hat{f}_{p} N_{t}=\frac{f_{p}N_{t}}{k_{h}w}$ (see Appendix A). Overall, we see that \emph{flex} mode of detachment shows the highest reduction factor among the three modes, with the optimal value of $\chi \sim 1$.

@@

The above analysis illustrates how the design of the beetle's hairy
adhesive pads is suitable for modulating its adhesion. Effective control
and release of its joints can help the insect to reduce the pad's
adhesion, allowing it to detach with little effort. High reduction
in adhesion is seen when the pad is tilted relative to the surface
during detachment, as a result of \emph{elastic weakening}. To the
best of our knowledge, there is no direct experimental evidence that
beetles or any other animal can modulate its adhesion by taking advantage of this effect.
Considering that hair deformation occurs at length scales below 10
\textgreek{m}m, direct observation of this effect on running beetles
would be challenging. A recent study on PDMS micro-pillar arrays,
however, does indeed show a strong reduction in the adhesion force
due to slight misalignments with the surface \cite{RN252}. Based on
previously reported microscopic investigation of freely walking dock
beetles \cite{RN83}, we argue that the following experimental observations
provide support to our proposed model: 1) The detachment was shown
to follow a three-dimensional twist of the leg, which suggests a complex
inhomogeneous deformation of hairs across the array, leading to \emph{elastic
weakening}, which is suited for easy detachment. Similar twisting action during detachment was also observed in flies \cite{niederegger2003} and has been used to easily detach mushroom-shaped artificial adhesive arrays \cite{kang2017}.  2) The beetle can at times instantaneously detach all
its legs and drop itself while upside down. This could be explained
by the beetle freeing up its joints and using just its body weight
to provide the necessary force to detach all its legs via \emph{free
pull} (similar to path 3 above). Lateral video recordings showed that in this scenario, claws were the last to detach when a leg loses contact with the surface, which also indicates a \emph{flex} mode of detachment (similar to path 5). 3) Only a fraction of the beetle's
pads made contact with the surface during locomotion, which indicates
that the pads should naturally be in a slightly tilted state. This
not only reduces the contact area, but also non-uniformly deforms
the hairs, both leading to a reduction in adhesion for easy detachment.
4) Contact images showed that the array \emph{peels} from the proximal
to distal direction during detachment. However, the beetle's hairs
are attached to a relatively stiff backing \cite{RN53}, so it wouldn't
be able to \emph{peel} its array, since peeling, strictly speaking,
depends on the elastic contribution of a thin flexible backing as
it bends during the process \cite{RN147}. Rather, the \emph{peeling}
observed in the beetle's case should be a result of the pad detaching
from the surface in a tilted orientation, causing the hairs to distinctly detach
in sequence. 5) The time scale of detachment was reported to be an
order of magnitude shorter than the attachment time scale, which could
be a result of the elastic recoil of the leg causing a spontaneous
propagation of the detachment front (Figure \ref{fig:Fixed-pull}).

There exists a limit to how much the pad can tilt, depending on its
geometry and material properties. Suppose the hair has a maximum linear
elastic strain limit, $\varepsilon_{m}$, and natural length, $l_{h,0}$.
Based on Figure \ref{fig:Schematic}, if the right most hair is compressed
to its elastic limit, one can derive from simple geometry, that, the
corresponding maximum limit in tilt angle is given by: 
\[
\theta_{limit}=\arctan\frac{l_{h,0}\varepsilon_{m}}{\left(N_{t}-1\right)w}
\]
$\theta_{limit}$ will limit the reduction factor for each of the
detachment mechanisms presented. Longer hairs can result in a lateral
collapse or bundling of hairs, imposing an additional constraint on
$\theta_{limit}$. Large deformation of hairs can also lead to buckling,
which will further limit the reduction in adhesion due to the smaller
effective modulus. Buckling could also, interestingly, promote easier detachment in the \emph{free pull} mode.  
When the compressed hairs at one end of the array buckle, 
there would be an excess clockwise moment in the array system (Figure \ref{fig:Free-pull}). 
This excess moment could subsequently drive the detachment of the remaining hairs.  In the case of biological systems, the ability of an insect to provide the load necessary to tilt and compress its hairy adhesive pad against the surface would further introduce limitations to follow any of the detachment modes discussed here.
All things considered, the geometry and elastic properties of the individual hairs are 
crucial parameters to consider in the design of an optimal array system which shows reversible adhesion via \emph{elastic weakening}.

@@

Controlled detachment of a fibrillar system similar to an insect's tarsal hairy adhesive pads can be achieved
by either 1) pulling the pad while maintaining a constant tilt angle,
2) pulling the pad while maintaining a free tibia-tarsus leg joint or 3) flexing
the pad around the claw. In all three scenarios, an inhomogeneous deformation of hairs across the array results in significant reductions
in the net adhesion due to an elastic effect. Strategic control of the joint's mobility or claw
can allow the leg to easily switch between the above mechanisms, thus
providing a simple way to reduce adhesion as per necessity. The presence
of a deformable leg can further trigger a spontaneous propagation
of hair detachment due to the leg's elastic recoil, making it suitable
for fast detachment. Arrays with low $\hat{f}_{p}$ and large number
of hairs, with a hair geometry that allows for large deformations
while avoiding buckling and lateral bundling represent the optimal
design conditions to maximize the range of control over adhesion.
The proposed model has been compared with previously reported experimental
observations of leg detachment in dock beetles and highlights possible role of the joint and claws to 
enable reversible adhesion. Similar strategies could potentially be adopted in the design of bio-inspired 
artificial fibrillar adhesives to easily switch the adhesion state without the need of asymmetric structures.
